Metrics

### 2023-12-15 src/plots.Rmd
Split plots by age group

    # Calc metric by cause of death
    if (by_cod) {

@@

        # Calc metric by cod
        for (cod in causes) {

            # Filter data for cod
            df_filter <- df %>% filter(physician_cghr10 == cod & is_agreed == TRUE)
            metric_name <- paste0(name, " COD Agree ", cod)

            # Calc metric for cod
            out[[metric_name]] <- calc_per_model(
                actual = df_filter %>%
                    pull(physician_cghr10),
                pred = df_filter %>%
                    select(ends_with("_cghr10"), -physician_cghr10),
                func = func,
                ...
            ) %>% rename(
                 {{ metric_name }} := Metric
            )
        }
    }

@@

        # Calc metric by age range
        for (ar in age_ranges) {

            # Filter for age range
            df_filter <- df %>% filter(age_range == ar & is_agreed == TRUE)
            metric_name = paste0(name, " Age Agree ", ar)

            # Calc metric for cod
            out[[metric_name]] <- calc_per_model(
                actual = df_filter %>%
                    pull(physician_cghr10),
                pred = df_filter %>%
                    select(ends_with("_cghr10"), -physician_cghr10),
                func = func,
                ...
            ) %>% rename(
                 {{ metric_name }} := Metric
            )
        }
    }

@@

# Create labels to axis titles
y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")

```

@@

Display a plot of cases by age range.

```{r, fig.height = 8, fig.width = 6}

# Format plot data
eardata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(age_range) %>%
    summarize(count = n()) %>%
    separate(
        age_range,
        into = c("age_range_value", "age_range_unit"),
        sep = " "
    ) %>%
    separate(
        age_range_value,
        into = c("age_range_min", "age_range_max"),
        sep = "-"
    ) %>%
    mutate(
        age_range_min = as.integer(age_range_min),
        age_range_max = as.integer(age_range_max),
        age_range_unit = factor(age_range_unit, levels = c(
            "Weeks",
            "Days",
            "Months",
            "Years"
        )),
        age_range_label = paste0(
            age_range_min,
            "-",
            age_range_max,
            " ",
            age_range_unit,
            "\n(n=", count, ", ", round((count / nagree) * 100), "%)"
        )
    ) %>%
    arrange(age_range_unit, age_range_min, age_range_max) %>%
    mutate(
        age_range_label = factor(age_range_label, levels = unique(age_range_label))
    )

# Plot the data
earplot <- eardata %>%
    ggplot(aes(x = age_range_label, y = count)) +
    geom_bar(
        stat = "identity",
        fill = "#1d1d1d",
        color = "white",
        width = 0.5
    ) +
    labs(
        y = y_title,
        x = element_blank()
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    ) +
    coord_flip()

# Save the plot
earplot
ggsave("../manuscript/fig-data-agerange.pdf", plot = earplot, dpi = 300)
```

@@

@@

Display a plot of performance for physician agreed records by age ranges.

```{r, fig.height = 11, fig.width = 8}

# Calc total agreed
nagree <- df %>% filter(is_agreed == TRUE) %>% nrow

# Get unique age range columns
arange_col <- out %>% select(starts_with("PCCC Age Agree ")) %>% names

@@

    # Get cod without prefix
    ar <- gsub("PCCC Age Agree ", "", ar_col)

    # Calc num and perc cases for age range
    narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
    parange <- (narange / nagree) * 100
    parange_label <- if (round(parange) >= 1) round(parange) else "<1"

@@

# Prepare boxplot data
ardata <- out %>%
    select(
        Model,
        starts_with("PCCC Age Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC Age Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "Age Range",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "Age Range" = recode(`Age Range`, !!!arange_remap)
    ) %>%
    group_by(`Age Range`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Plot boxplot
arplot <- ardata %>%
    ggplot(aes(x = `Age Range`, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 1,
        position = position_nudge(y = -0.065)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 0,
        position = position_nudge(y = 0.065)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.03),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.03),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%)"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(0.1, 1) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_blank(),
        axis.line.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            color = "black",
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        )
    )

# Save the plot
arplot
ggsave("../manuscript/fig-perf-agerange.pdf", plot = arplot, dpi = 300)
```

@@

```{r, fig.height = 16.5, fig.width = 8}

# Calc total agreed
nagree <- df %>% filter(is_agreed == TRUE) %>% nrow

# Get unique cause columns
causes_col <- out %>% select(starts_with("PCCC COD Agree ")) %>% names

@@

    # Get cod without prefix
    cod <- gsub("PCCC COD Agree ", "", cod_col)

@@

# Prepare boxplot data
coddata <- out %>%
    select(
        Model,
        starts_with("PCCC COD Agree ")
    ) %>%
    rename_at(
         vars(-Model),
         ~gsub("PCCC COD Agree ", "", .)
    ) %>%
    filter(!str_detect(Model, "&")) %>% # remove multi models
    pivot_longer( # transform to long format
        cols = -Model,
        names_to = "COD",
        values_to = "PCCC"
    ) %>%
    mutate( # rename cod with counts
        "COD" = recode(`COD`, !!!cod_remap)
    ) %>%
    group_by(`COD`) %>%
    mutate( # Make values less than 0 equal to 0
        PCCC = if_else(PCCC <= 0, 0, PCCC)
    ) %>%
    mutate( # Add min, mid, and max model names to label
        "PCCC Min" = if_else(
            PCCC <= min(PCCC) + 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Max" = if_else(
            PCCC >= max(PCCC) - 0.05,
            paste0(
                Model,
                if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
            ),
            NA
        ),
        "PCCC Mid" = if_else(
            is.na(`PCCC Min`) & is.na(`PCCC Max`),
            paste0(Model, "\n(", round(PCCC, 2), ")"),
            NA
        ),
        "PCCC Min" = if_else( # Combine into one row if close PCCC
            `PCCC` == min(PCCC),
            if_else(
                sum(!is.na(`PCCC Min`)) > 1,
                paste0(na.omit(`PCCC Min`), collapse = "\n"),
                paste0(
                    str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                    collapse = "\n"
                )
            ),
            NA
        ),
        "PCCC Max" = if_else(
            `PCCC` == max(PCCC),
            if_else(
                sum(!is.na(`PCCC Max`)) > 1,
                paste0(na.omit(`PCCC Max`), collapse = "\n"),
                paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                       collapse = "\n")
            ),
            NA
        )
    )

@@

# Plot boxplot
codplot <- coddata %>%
    ggplot(aes(x = COD, y = PCCC)) +
    geom_boxplot(
        linewidth = 0.5,
        width = 0.25
    ) +
    geom_text(
        aes(label = `PCCC Min`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 1,
        position = position_nudge(y = -0.12)
    ) +
    geom_text(
        aes(label = `PCCC Max`),
        color = "#4d4d4d",
        size = 2.5,
        hjust = 0,
        position = position_nudge(y = 0.12)
    ) +
    stat_summary( # min pccc txt on boxplot
        geom = "text",
        fun = min,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = -0.06),
        size = 3
    ) +
    stat_summary( # max pccc txt on boxplot
        geom = "text",
        fun = max,
        aes(label = sprintf("%1.2f", after_stat(y))),
        position = position_nudge(y = 0.06),
        size = 3
    ) +
    labs(
        x = paste0("Physician Agreed Records (n=", nagree, ", 100%) for ", length(causes_col), " Causes of Death"),
        y = "PCCC (0=Low, 1=High)"
    ) +
    ylim(-0.3, 1.3) +
    coord_flip() +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.line = element_blank(),
        axis.line.y = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10)),
        axis.line.x = element_line(
            color = "black",
            arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
        )
    )

# Save the plot
codplot
ggsave("../manuscript/fig-perf-cod.pdf", plot = codplot, dpi = 300)
```

>>>>

    # Calc metric by cause of death for each age group
    if (by_cod) {

@@

        # Calc metric by cod
        for (a in c("adult", "child", "neo")) {
            for (cod in causes) {

                # Filter data for cod
                df_filter <- df %>% filter(
                    physician_cghr10 == cod & is_agreed == TRUE & age == a
                )
                metric_name <- sprintf(
                    "%s %s COD Agree %s", name, str_to_title(a), cod
                )

                # Calc metric for cod
                if (nrow(df_filter) > 0) {
                    out[[metric_name]] <- calc_per_model(
                        actual = df_filter %>%
                            pull(physician_cghr10),
                        pred = df_filter %>%
                            select(ends_with("_cghr10"), -physician_cghr10),
                        func = func,
                        ...
                    ) %>% rename(
                         {{ metric_name }} := Metric
                    )
                }
            }
        }
    }

@@

        # Calc metric by age range
        for (a in c("adult", "child", "neo")) {
            for (ar in age_ranges) {

                # Filter for age range
                df_filter <- df %>% filter(
                    age_range == ar & is_agreed == TRUE & age == a
                )
                metric_name <- sprintf(
                    "%s %s Age Agree %s", name, str_to_title(a), ar
                )

                # Calc metric for cod
                if (nrow(df_filter) > 0) {
                    out[[metric_name]] <- calc_per_model(
                        actual = df_filter %>%
                            pull(physician_cghr10),
                        pred = df_filter %>%
                            select(ends_with("_cghr10"), -physician_cghr10),
                        func = func,
                        ...
                    ) %>% rename(
                         {{ metric_name }} := Metric
                    )
                }
            }
        }
    }

@@

# Create labels to axis titles
y_title <- paste0("Physician Agreed Records (n=", nagree, ", 100%)")
```

@@

Display a plot for each age group of cases by age range.

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")

    # Format plot data
    eardata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(age_range) %>%
        summarize(count = n()) %>%
        separate(
            age_range,
            into = c("age_range_value", "age_range_unit"),
            sep = " "
        ) %>%
        separate(
            age_range_value,
            into = c("age_range_min", "age_range_max"),
            sep = "-"
        ) %>%
        mutate(
            age_range_min = as.integer(age_range_min),
            age_range_max = as.integer(age_range_max),
            age_range_unit = factor(age_range_unit, levels = c(
                "Weeks",
                "Days",
                "Months",
                "Years"
            )),
            age_range_label = paste0(
                age_range_min,
                "-",
                age_range_max,
                " ",
                age_range_unit,
                "\n(n=", count, ", ", round((count / arows) * 100), "%)"
            )
        ) %>%
        arrange(age_range_unit, age_range_min, age_range_max) %>%
        mutate(
            age_range_label = factor(age_range_label, levels = unique(age_range_label))
        )

    # Plot the data
    earplot <- eardata %>%
        ggplot(aes(x = age_range_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10))
        ) +
        coord_flip()

    # Save the plot
    print(earplot)
    ggsave(
        sprintf("../manuscript/fig-data-agerange-%s.pdf", a),
        plot = earplot,
        dpi = 300
    )
}
```

@@

Display a plot for each age group of cases by cause of death.

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")

    # Format plot data
    ecoddata <- df %>%
        filter(is_agreed == TRUE & age == a) %>%
        group_by(physician_cghr10) %>%
        summarize(count = n()) %>%
        mutate(
            cod_label = paste0(
                if_else(
                    str_count(physician_cghr10, "\\s+") > 3,
                    str_replace(physician_cghr10, "(\\S+\\s+\\S+\\s+\\S+) ", "\\1\n"),
                    physician_cghr10
                ),
                "\n(n=", count, ", ",
                if_else(
                    ((count / arows) * 100) < 1,
                    "<1",
                    as.character(round((count / arows) * 100))
                ), "%)"
            )
        ) %>%
        arrange(count) %>%
        mutate(
            cod_label = factor(cod_label, levels = unique(cod_label))
        )

    # Plot the data
    ecodplot <- ecoddata %>%
        ggplot(aes(x = cod_label, y = count)) +
        geom_bar(
            stat = "identity",
            fill = "#1d1d1d",
            color = "white",
            width = 0.5
        ) +
        labs(
            y = atitle,
            x = element_blank()
        ) +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.text.x = element_text(hjust = 1)
        ) +
        coord_flip()

    # Save the plot
    print(ecodplot)
    ggsave(
        sprintf("../manuscript/fig-data-cod-%s.pdf", a),
        plot = ecodplot,
        dpi = 300,
        width = if (a == "adult") 6 else NA,
        height = if (a == "adult") 8 else NA
    )
}
```

@@

Display a plot for each age group of performance for physician agreed records by age ranges.

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label and ref for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- if (a == "neo") {
        paste0("Physician Agreed\n", alabel, " Records\n(n=", arows, ", 100%)")
    } else {
        paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    }
    aref <- str_to_title(a)

    # Get unique age range columns
    arange_col <- out %>% select(starts_with(sprintf(
            "PCCC %s Age Agree ",
            aref
        ))) %>%
        names

@@

        # Get cod without prefix
        ar <- gsub(sprintf("PCCC %s Age Agree ", aref), "", ar_col)

        # Calc num and perc cases for age range
        narange <- df %>% filter(age_range == ar & is_agreed == TRUE) %>% nrow
        parange <- (narange / arows) * 100
        parange_label <- if (round(parange) >= 1) round(parange) else "<1"

@@

    # Prepare boxplot data
    ardata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s Age Agree", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s Age Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "Age Range",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "Age Range" = recode(`Age Range`, !!!arange_remap)
        ) %>%
        group_by(`Age Range`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

@@

    # Plot boxplot
    arplot <- ardata %>%
        ggplot(aes(x = `Age Range`, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.065)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.065)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.03),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.03),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(0.1, 1) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )

    # Save the plot
    print(arplot)
    ggsave(
        sprintf("../manuscript/fig-perf-agerange-%s.pdf", a),
        plot = arplot,
        dpi = 300,
        width = if (a == "adult") 6 else if (a == "neo") 6 else NA,
        height = if (a == "adult") 8 else if (a == "neo") 2.5 else NA
    )
}
```

@@

```{r}
for (a in c("adult", "child", "neo")) {

    # Create label for age group
    arows <- df %>% filter(is_agreed == TRUE & age == a) %>% nrow
    alabel <- if (a == "neo") "Neonatal" else str_to_title(a)
    atitle <- paste0("Physician Agreed ", alabel, " Records (n=", arows, ", 100%)")
    aref <- str_to_title(a)

    # Get unique cause columns
    causes_col <- out %>% select(starts_with(sprintf(
        "PCCC %s COD Agree ", aref
    ))) %>% names

@@

        # Get cod without prefix
        cod <- gsub(sprintf("PCCC %s COD Agree ", aref), "", cod_col)

@@

    # Prepare boxplot data
    coddata <- out %>%
        select(
            Model,
            starts_with(sprintf("PCCC %s COD Agree ", aref))
        ) %>%
        rename_at(
             vars(-Model),
             ~gsub(sprintf("PCCC %s COD Agree ", aref), "", .)
        ) %>%
        filter(!str_detect(Model, "&")) %>% # remove multi models
        pivot_longer( # transform to long format
            cols = -Model,
            names_to = "COD",
            values_to = "PCCC"
        ) %>%
        mutate( # rename cod with counts
            "COD" = recode(`COD`, !!!cod_remap)
        ) %>%
        group_by(`COD`) %>%
        mutate( # Make values less than 0 equal to 0
            PCCC = if_else(PCCC <= 0, 0, PCCC)
        ) %>%
        mutate( # Add min, mid, and max model names to label
            "PCCC Min" = if_else(
                PCCC <= min(PCCC) + 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(min(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Max" = if_else(
                PCCC >= max(PCCC) - 0.05,
                paste0(
                    Model,
                    if_else(round(PCCC, 2) != round(max(PCCC), 2), paste0(" (", round(PCCC, 2), ")"), "")
                ),
                NA
            ),
            "PCCC Mid" = if_else(
                is.na(`PCCC Min`) & is.na(`PCCC Max`),
                paste0(Model, "\n(", round(PCCC, 2), ")"),
                NA
            ),
            "PCCC Min" = if_else( # Combine into one row if close PCCC
                `PCCC` == min(PCCC),
                if_else(
                    sum(!is.na(`PCCC Min`)) > 1,
                    paste0(na.omit(`PCCC Min`), collapse = "\n"),
                    paste0(
                        str_replace(na.omit(`PCCC Min`), "\\s*\\(.*\\)", ""),
                        collapse = "\n"
                    )
                ),
                NA
            ),
            "PCCC Max" = if_else(
                `PCCC` == max(PCCC),
                if_else(
                    sum(!is.na(`PCCC Max`)) > 1,
                    paste0(na.omit(`PCCC Max`), collapse = "\n"),
                    paste0(str_replace(na.omit(`PCCC Max`), "\\s*\\(.*\\)", ""),
                           collapse = "\n")
                ),
                NA
            )
        )

@@

    # Plot boxplot
    codplot <- coddata %>%
        ggplot(aes(x = COD, y = PCCC)) +
        geom_boxplot(
            linewidth = 0.5,
            width = 0.25
        ) +
        geom_text(
            aes(label = `PCCC Min`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 1,
            position = position_nudge(y = -0.12)
        ) +
        geom_text(
            aes(label = `PCCC Max`),
            color = "#4d4d4d",
            size = 2.5,
            hjust = 0,
            position = position_nudge(y = 0.12)
        ) +
        stat_summary( # min pccc txt on boxplot
            geom = "text",
            fun = min,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = -0.06),
            size = 3
        ) +
        stat_summary( # max pccc txt on boxplot
            geom = "text",
            fun = max,
            aes(label = sprintf("%1.2f", after_stat(y))),
            position = position_nudge(y = 0.06),
            size = 3
        ) +
        labs(
            x = atitle,
            y = "PCCC (0=Low, 1=High)"
        ) +
        ylim(-0.3, 1.3) +
        coord_flip() +
        theme_minimal() +
        theme(
            panel.grid = element_blank(),
            axis.line = element_blank(),
            axis.line.y = element_blank(),
            axis.title.x = element_text(margin = margin(t = 10)),
            axis.title.y = element_text(margin = margin(r = 10)),
            axis.line.x = element_line(
                color = "black",
                arrow = grid::arrow(length = unit(0.2, "cm"), ends = "both")
            )
        )

    # Save the plot
    print(codplot)
    ggsave(
        sprintf("../manuscript/fig-perf-cod-%s.pdf", a),
        plot = codplot,
        dpi = 300,
        width = if (a == "adult") 8 else NA,
        height = if (a == "adult") 10 else NA
    )
}
```
